### 2018-06-22 Stickleback_Paper.tex
latest plots

Note: Finish after the whole paper has been written

@@

Our models are forward-moving evolutionary models which
emulate the geography, selective pressure, and genomic architecture 
of coastal marine and freshwater lake populations. 
Here we give a brief overview of the software used and the models created to observe the effects of selection.

\todo{Each set of simulations was run multiple times to ensure the data we observed was not stochastic.}

Note: Maybe talk about some things are stochastic: 
(1) Correlation of mutation frequencies at low migration rates
(2) Distribution of Effect Size? (run another set to make sure)

@@

%FIGURES THAT SHOW THIS:
%-Time to adaptation
%\begin{figure}[h!tb]
%	\begin{center}
%  		\includegraphics[width=01.0\linewidth]{???}
%  		\caption{A boat.}
%  		\label{fig:boat1}
%	\end{center}
%\end{figure}

@@

\bibliography{Citations}{}
\bibliographystyle{plain}

>>>>

\todo{Do last.}

@@

Our models are forward-moving evolutionary models which
emulate the geography, selective pressure, and genomic architecture 
of coastal marine and freshwater lake populations. 
Here we give a brief overview of the software used and the models created to observe the effects of selection. 
Each set of simulations was run multiple times to ensure the data we observed was ???

%(1) Correlation of mutation frequencies at low migration rates
%(2) Distribution of Effect Size? (run another set to make sure)

@@

%FIGURES THAT SHOW THIS:
%-Time to adaptation
\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=01.0\linewidth]{matplotlib/TimeToAdaptation.png}
  		\caption{A boat.}
  		\label{fig:boat1}
	\end{center}
\end{figure}

@@

\newpage
\bibliography{Citations}{}
\bibliographystyle{plain}
